---
title: "Assignment8"
author: "KUN LIU"
date: "2020/10/31"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1
Consider the Ornstein-Uhlenbeck process
$$dr(t) = \alpha(b-r(t))dt + \sigma dW(t), $$
In Vasicek model, 
$$r(t_{i+1}) = e^{H(t_{i+1})-H(t_{i})}r(t_{i})+\mu(t_{i},t_{i+1})+\sigma_{r}(t_{i},t_{i+1})Z_{i+1},$$
where $t_{i+1} = t_{i}+\triangle$,
$H(t_{i+1})-H(t_{i}) = -\alpha\triangle$,
$\mu(t_{i},t_{i+1}) = b\alpha\int_{t_{i}}^{t_{i+1}}e^{-\alpha (t_{i+1}-s)}ds = b(1-e^{-\alpha\triangle}),$
$\sigma_{r}(t_{i},t_{i+1}) = \frac{\sigma}{\sqrt{2\alpha}}\sqrt{1-e^{-2\alpha\triangle}},$
$Z_{i+1} \sim N(0,1).$


Let t denotes t$_{i}$, t+$\triangle$ denotes t$_{i+1}$. Then
$$r(t+\triangle) = e^{-\alpha\triangle}r(t)+b(1-e^{-\alpha\triangle})+ \frac{\sigma}{\sqrt{2\alpha}}\sqrt{1-e^{-2\alpha\triangle}}Z,$$ 
where Z$\sim$ N(0,1).

# 2

```{r}
r0 = 1
T = 500
step = 1/500

ou_process = function(alpha,sigma,b,r0,T,step)
{ r = c(r0)
  times = T/step
 for(i in (1:times))
 {last_r = r[i]
  q1 = exp(-alpha*step)*last_r
  q2 = b*(1-exp(-alpha*step))
  q3 = sigma/(2*alpha)^0.5 * (1-exp(-2*alpha*step))^0.5
  z = rnorm(1)
  r[i+1] = q1+q2+q3*z
 }
plot(x=seq(0,T,by=step),y=r,main = '',xlab = 'time',ylab = 'sample')
}

```

I construct the 18 sample paths in one figure.
```{r}
par(mfrow=c(3,6))
for (alpha in c(0.1,1,5))
{for (sigma in c(0.1,0.2,0.5))
  {for (b in c(-5,5))
    {ou_process(alpha,sigma,b,r0=1,T=500,step=1/500)
      
    }
    
  }
}
```

From the 18 sample paths, I find that when $\alpha$ increases, the path tends to be steady; while when $\sigma$ increases, the path tends to be fluctuant.

# 3
Consider $\alpha=1$,$\sigma=0.5$,b=5,r$_{0}$ = 1.
```{r}
em = function(size,delta,alpha,sigma,b,r0)
{r1 = c()
 times = 1/delta
 for (i in (1:1000))
   {last_r = r0
  for (j in (1:times))
 {mean = last_r+alpha*(b-last_r)*delta
  sd = delta*sigma 
  last_r = rnorm(n=1,mean=mean,sd=sd)
 }
   r1[i] = last_r
 }
   plot(density(r1),xlab = '',ylab = '',main = 'kernel density')
  
}
```

When $\delta$ =1, the kernel density is 
```{r}
em(size=1000,delta=1,alpha=1,sigma=0.5,b=5,r0=1)
```
When $\delta$ =0.5, the kernel density is 
```{r}
em(size=1000,delta=0.5,alpha=1,sigma=0.5,b=5,r0=1)
```
When $\delta$ =0.1, the kernel density is 
```{r}
em(size=1000,delta=0.1,alpha=1,sigma=0.5,b=5,r0=1)
```
When $\delta$ =0.01, the kernel density is 
```{r}
em(size=1000,delta=0.01,alpha=1,sigma=0.5,b=5,r0=1)
```




